Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-06 R0V0.tex
Add a reference for the number of monomials
Reduce the size of the equation describing the dynamical system of the example to fit in the page. Start to write about distributed design.

The property described in item 2 of Problem \ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology). Consider the network composed of systems described by the following equation.
\begin{equation}\label{eq:example}
	\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i.
	\end{array}\right.
\end{equation}
As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to the number of variables. However, by exploring sparsity, up to 512 of theses systems can be connected and the controller can be computed.

@@

@@

\section{Illustration}\label{sec:Illustration}

A case where structured controller design is relevant is on distributed design for network systems. Let $N>0$ be a constant integer, consider the graph describing the network structure in Figure~\ref{fig:graph}.
\begin{figure}[htpb!]
	\centering
	\input{./imgs/GraphStructure.pdf_tex}
	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
	\label{fig:graph}
\end{figure}
For each index $i\in\mathbb{N}_{[1,N]}$, the agents dynamics is described by the system
\begin{equation}\tag{\ref{eq:example}}
	\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i,
	\end{array}\right.
\end{equation}
where for convenience $x_0=x_1$ and $x_N=x_{N+1}$.

@@

When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}\;.
\end{equation*}
Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
N^2\begin{pmatrix}
n+d\\ d
\end{pmatrix}^2
\end{equation*}
equations to be solved. This motivates the approach proposed in this paper.

>>>>

The property described in item 2 of Problem \ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology). Consider the network composed of systems described by the following equation.
\begin{equation}\label{eq:example}
	\scalebox{0.95}{$\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i.
	\end{array}\right.$}
\end{equation}
As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to the number of variables. However, by exploring sparsity, up to 512 of theses systems can be connected and the controller can be computed.

@@

Before showing how the MI \eqref{eq:MI formulation} can be computed in parallel, some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015}.

Consider a graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{clique tree} is a tree that has cliques as its nodes. An algorithm to compute the number of cliques is provided in \cite{BronKerbosch1973}.

@@

\section{Numerical Experiment}\label{sec:Illustration}

A case where structured controller design is relevant is on distributed design for network systems. Let $N>0$ be a constant integer, consider the graph describing the network structure in Figure~\ref{fig:graph}.
\begin{figure}[htpb!]
	\centering
	\input{./imgs/GraphStructure.pdf_tex}
	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
	\label{fig:graph}
\end{figure}
For each index $i\in\mathbb{N}_{[1,N]}$, the agents dynamics is described by the system
\begin{equation}\tag{\ref{eq:example}}
	\scalebox{0.95}{$\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i,
	\end{array}\right.$}
\end{equation}
where for convenience $x_0=x_1$ and $x_N=x_{N+1}$.

@@

When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
N^2\begin{pmatrix}
n+d\\ d
\end{pmatrix}^2
\end{equation*}
equations to be solved. This motivates the approach proposed in this paper.
